Trans-Dimensional Bayesian Inference for Gravitational Lens Substructures

### 2015-09-09 Papers/ms.tex

\begin{figure}
\begin{center}
\includegraphics[scale=0.8]{sources.pdf}
\caption{Three example sources (and the corresponding lensed, blurred images)
representative of the posterior distribution. All three lens system scenarios
have substructures, which cause subtle distortions from the usual shape of
the caustics and critical curves (plotted as black curves).
The angular scales are 3 arcseconds for the sources and 15
arcseconds for the images.
\label{fig:sources}}
\end{center}
\end{figure}

>>>>

\begin{figure*}
\begin{center}
\includegraphics[scale=0.8]{sources.pdf}
\caption{Three example sources, the density profile in substructures,
and the corresponding lensed, blurred images,
representative of the posterior distribution.
The angular scales are 7.5 arcseconds for the sources and 15
arcseconds for the images.
\label{fig:sources}}
\end{center}
\end{figure*}
